Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-09-05 paper/paper.tex
minor changes

{\bf Motivated by observations of other CDGs
  that show gas kinematics ranging from pure rotation and low velocity
dispersion to high velocity dispersion without rotation
\citep{2015A&A...577A..21C,2017A&A...600A.125C} we perform here a new
study to explain \tol's \lya emission features under two physical
conditions for the interstellar medium: multiphase outflows and pure rotation.}

@@

In the next section we review the observational characteristics of
\tol, then we summarize the main features in the multiphase and
rotation models to explain how we fit their free parameters 
to the \tol's \lya line shape.
We use the results to interpret them in terms of the galaxy's
dynamical mass and argue why the multiphase model should be preferred
over the rotation model.

@@

The low p-values are illustrated by the results shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the $1\%$ models with the lowest
$\chi^2/d.o.f.$, where we use the total number of degrees of freedom,
$d.o.f.=104$. 
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump, {\bf
  with the minimum $\chi^2/d.o.f.=11.7$.}

@@

{\bf These results disfavor the high rotational velocity of $V_{m}\sim350$
\kms\  that we find in the pure rotation model. 
On the other hand the results from the multiphase model yield a
velocity dispersion $\sigma_{\rm cl}=$\sigmaclump, consistent with observed
values in other CDG, favoring the multiphase model.}
In this case we can  estimate a value for the dynamical
mass using the constraints for the velocity dispersion, $\sigma$,  in
a spherical system localized in a region of size $r$

@@

A larger dynamical mass estimate over its baryonic mass is a hint that
\tol\ is dark matter dominated.  
Following the methodology of \citet{2011ApJ...726..108T} we estimate
that a dark matter halo with a virial mass $\sim 6\times 10^{11}$
M$_{\odot}$ {\bf and a virial radius $220$ kpc } could explain this dynamical mass.
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the median mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.  
Figure \ref{fig:mass} shows the enclosed mass as a function of radius
for different dark matter halos together with the \tol's dynamical
mass estimate. 
{\bf This should be considered an an upper bound as lower values
  could be achieved if one considers instead a cored profile.}
{\bf Realistic mass estimates could only be achieved by detailed mass
  modelling once \tol's full rotation curve   becomes available.}

{\bf New IFU observations are needed to confirm \tol's kinematics.
This could be done with the Multi Unit Spectroscopic Explorer (MUSE) 
\citep{2014Msngr.157...13B}, the Gemini Multi-Object Spectrographs (GMOS) 
\citep{2004PASP..116..425H} or the Fibre Large Array Multi Element
Spectrograph (FLAMES) \citep{2002Msngr.110....1P} as they have the spatial
resolution, spectral coverage and field of view required to produce
H$\alpha$ velocity maps to perform the kind of study presented by
\citet{2015A&A...577A..21C} on CDGs or \citet{Herenz16} on nearby
\lya\ emitting galaxies.}

>>>>

{\bf Motivated by observations of other CDGs
  that show gas kinematics ranging from pure rotation and low velocity
dispersion to high velocity dispersion without a clear rotation pattern
\citep{2015A&A...577A..21C,2017A&A...600A.125C} we perform here a new
study to explain \tol's \lya emission features under two physical
conditions for the interstellar medium: multiphase outflows and pure rotation.}

@@

In the next section we review the observational characteristics of
\tol, then we summarize the main features in the multiphase and
rotation models to explain how we fit their free parameters 
to the \tol's \lya line shape.
We use the results to interpret them in terms of the galaxy's
dynamical mass and argue why in this case the multiphase model should
be preferred over the rotation model.

@@

The low p-values are illustrated by the results shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the $1\%$ models with the lowest
$\chi^2/d.o.f.$, where we use the total number of degrees of freedom,
$d.o.f.=104$. 
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump, {\bf
  with the inimum $\chi^2/d.o.f.=11.7$.}

@@

{\bf These results disfavor the high rotational velocity of $V_{m}\sim350$
\kms\  that we find in the pure rotation model. 
On the other hand the results from the multiphase model yield a
velocity dispersion $\sigma_{\rm cl}=$\sigmaclump, consistent with observed
values in other CDGs, favoring the multiphase model.}
In this case we can  estimate a value for the dynamical
mass using the constraints for the velocity dispersion, $\sigma$,  in
a spherical system localized in a region of size $r$

@@

A larger dynamical mass estimate over its baryonic mass is a hint that
\tol\ is dark matter dominated.  
Following the methodology of \citet{2011ApJ...726..108T} we estimate
that a dark matter halo with a virial mass $\sim 6\times 10^{11}$
M$_{\odot}$ {\bf and a virial radius $220$ kpc } could explain this dynamical mass.
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the median mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.  
Figure \ref{fig:mass} shows the enclosed mass as a function of radius
for different dark matter halos together with the \tol's dynamical
mass estimate. 
{\bf This should be considered an an upper bound as lower values
  could be achieved if one considers instead a cored DM profile.}
{\bf Realistic mass estimates could only be achieved by detailed mass
  modelling once \tol's detailed kinematic information becomes
  available.}

{\bf New IFU observations are needed to confirm \tol's kinematics.
This could be done with the Multi Unit Spectroscopic Explorer (MUSE) 
\citep{2014Msngr.157...13B}, the Gemini Multi-Object Spectrographs (GMOS) 
\citep{2004PASP..116..425H} or the Fibre Large Array Multi Element
Spectrograph (FLAMES) \citep{2002Msngr.110....1P} as they have the spatial
resolution ($\sim0.5^{\prime\prime}$), spectral coverage and field
of view required to produce H$\alpha$ velocity maps to perform the
kind of study presented by \citet{2015A&A...577A..21C} on CDGs or by
\citet{Herenz16} on nearby \lya\ emitting galaxies.}
